---
title: 'MATH 498 HW1'
author: "Drew Remmenga"
output:
  pdf_document: default
  html_notebook: default
---
```{r}
library(fda)
```
1.1
Assume that the median value does not have the maximum depth. Let b be the value with the maximum depth. a is the median yet lays exactly between fifty percent of the data. a is therefore deeper than b. This produces a contradiction so a must equal b. 
2.1
Consider the values directly above and below the deepest value. Call them $$z_{p-1}$$ and $$z_{p+1}$$. Now consider the log transformation. $$log(z_{p-1}) < log(y_{p}) < log(y_{p+1})$$. This demonstrates that under this transformation the deepest value remains the deepest value.
2.2
Consider the functions $$z_{p-1}$$ and $$z_{p+1}$$. For each of these functions if $$y_{p-1} < y_{p} < y_{p+1}$$ then $$z_{p-1} < z_{p} < z_{p+1}$$. So the depth of z_{i} = the depth of y_{i}.
```{r}
load("C:/Users/Drewr/Documents/School/MATH498/HW1/BB10K.rda")
split<- as.matrix(BB10K[,4 + 1:6])
split <- t( split)
indM<- BB10K$DIV == "M30"
indF<- BB10K$DIV == "F30"
split30F<- split[,indF]
timeF30<- BB10K$TIME[indF]
split30M<- split[,indM]
```
3.1
Split30F is functional based on times, the split, and the mile. You can tell it's a function because each data point has neighbors and a unique vertical position.
3.2
There is missing data to the function.
3.3
```{r}
boxplot(t(split30F))
```
There are outliers based on the classic boxplot criteria.
3.4
```{r}
fbplot(t(split30F))
```
There are outliers based on the functional boxplot. This gives some insight into how the function actually looks as well as the median function.
4.1
```{r}
split30FCentered <- scale(split30F, center=TRUE, scale=FALSE)
fbplot(t(split30FCentered))
```
There is not a relationship between depth and runners split times. For outliers there is. 